---
title: "Machine Learning Project"
author: "Cassie"
date: "October 9, 2017"
output: html_document
---

### This report will look at athletic tech wear data and, using training data, build a model to predict which exercise is being performed based on the other metrics. 

## Set working directory
```{r, echo = TRUE}
setwd("~/Coursera/R Repository/Machine Learning")
```

## Load Packages
```{r, echo = TRUE}
library(caret)
library(kernlab)
library(rpart)
library(rpart.plot)
library(RColorBrewer)
library(rattle)
library(randomForest)
library(e1071)
```

## Reading in the training and testing data
```{r, echo = TRUE}
testing <- read.csv("pml-testing.csv", na.strings=c("NA", "#DIV/0", ""))
training <- read.csv("pml-training.csv", na.strings=c("NA", "#DIV/0!", ""))
```

## Finding columns with NAs
```{r, echo = TRUE}
NAs <- colMeans(is.na(training))
table(NAs)
```

## Removing columns with NAs
```{r, echo = TRUE}
sum(as.logical(NAs))
colNAs <- !NAs
sum(colNAs)
train.NA <- training[colNAs]
str(train.NA)
```

## Getting rid of other unecessary columns
```{r, echo = TRUE}
others <- grep("^X$|user_name|timestamp|window", names(train.NA))
train.clean <- train.NA[-others]
```

## Data partioning for training and testing 
```{r, echo = TRUE}
set.seed (1)
inTrain <- createDataPartition(train.clean$classe, p=0.6, list=FALSE)
train <- train.clean[inTrain, ]
test <- train.clean[-inTrain, ]
```


## Testing different prediction models to determine which one has the highest accuracy. 

## 1. Prediction with decision tree
```{r, echo = TRUE}
model.1 <- rpart(classe~., data=train, method="class")
fancyRpartPlot(model.1)
predict.1 <- predict(model.1, test, type ="class")
confusionMatrix(predict.1, test$classe)
```

## 2. Prediction with random forest
```{r, echo = TRUE}
model.2 <- randomForest(classe~., data=train, method = "class")
predict.2 <- predict(model.2, test, type="class")
confusionMatrix(predict.2, test$classe)
```

### The random forest model has a higher accuracy rate so we will use that for the prediction model. 




